\documentclass{cv} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0.2in,right=0.4 in,bottom=0.2in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.1667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Lawrence Lim}
\address{+86 189 1752 5187 \\ \href{mailto:ll4715@nyu.edu}{ll4715@nyu.edu} \\ New York, NY}
\address{Homepage: \href{https://lawrencelim.xyz/}{lawrencelim.xyz} \\
	Github: \href{https://github.com/larry-lime}{larry-lime} \\
	LinkedIn: \href{https://www.linkedin.com/in/lawrence-rx-lim/}{lawrence-rx-lim}}

\begin{document}

%----------------------------------------------------------------------------------------
% Education Section
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

	\textbf{New York University} \hfill Expected Completion: Sep 2021 - May 2025\\
	Bachelor's Degree, Computer Science Major \hfill \textit{Shanghai, China}
	\begin{itemize}
		\item Cumulative GPA - 3.83/4.00; Major GPA - 3.85/4.00
	\end{itemize}

	% TODO: Update this so that it matches with LinkedIn
	\textbf{SJTU-THU-PKU Summer Program} \hfill July 2023\\
	Bachelor's Degree, Computer Science Major \hfill \textit{Shanghai, China}
	\begin{itemize}
		\item Course List: Cryptography and Blockchain, Artificial Intelligence
	\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% Work Experience Section
%----------------------------------------------------------------------------------------

\begin{rSection}{WORK EXPERIENCE}

	\textbf{Software Engineer Intern} \hfill Mar 2023 - Present\\
	Knn3 – User-centric DataFi solution for d/Apps and smart contracts  \hfill \textit{(Remote) Singapore}
	% TODO: Have some provable increase in performance metric. Replace second item with benchmark results
	\begin{itemize}
		\item Prototyped and researched Natural Language (NL) to SQL conversion methods leveraging LLM prompt chaining
		\item Built testing benchmark to evaluate the accuracy, speed, and cost of methods for generating SQL from NL
		\item Significanly improved benchmark performance by leveraging sentence transformers, Redis Cosine similarity search
		\item Containerized application with Docker, automated building, testing, and deployment to AWS with Jenkins CI/CD
	\end{itemize}

	\textbf{Technology Consultant Intern} \hfill Sep 2022 - May 2023\\
	Jika.io – Social community platform built for investors \hfill \textit{(Remote) Tel Aviv, Isreal}
	\begin{itemize}
		\item Constructed MongoDB to Google Bigquery data pipeline. Enabled data analysis and visualization with SQL
		\item Played primary role in designing relational schema and orchestrating each step of the ETL process
	\end{itemize}

	\textbf{Blockchain Research Analyst} \hfill May 2022 - Sep 2022 \\
	TokenInsight \hfill \textit{Shanghai, China}
	\begin{itemize}
		\item Research topics include zero-knowledge-proof rollups, optimistic rollups, and Ethereum’s development timeline.
		\item Wrote technical articles on various blockchain protocols and architecture. Also researched blockchain valuation and risk assessment. Served as core member of TokenInsight’s research team.
	\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Personal Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}

	% TODO: Elaborate on this
	\textbf{Airline Booking System – Full Stack Python Flask Application \href{https://github.com/larry-lime/airline-ticket-system}{View Project}}
	\begin{itemize}
		\item Leveraged Flask, MySQL database, and Bootstrap CSS to create an airline booking system inspired by Expedia.com
		\item Utilizes functions such as session tokens, user password hashing, and SQL triggers. Deployed on Railway.app
	\end{itemize}

	\textbf{Decentralized Crowd Funding – Full Stack Solidity and JavaScript d/App \href{https://lawrencelim.xyz/project/hh-fund-me/}{View Project}}
	\begin{itemize}
		\item Full stack Ethereum crowd funding app with Solidity and Hardhat for backend, and HTML/CSS/JS for frontend.
		\item Uses Chainlink Price Feeds for off-chain data with MetaMask and Ethereum Provider API for user payments.
	\end{itemize}

	\textbf{MeChat – Python GUI Desktop Chat App \href{https://lawrencelim.xyz/project/mechat/}{View Project}}
	% NOTE: I should probably remove Tkinter here. it's note impressive
	\begin{itemize}
		\item Utilizes web sockets for communication, end-to-end RSI encryption for security, and client-side multi-threading.
		\item Uses Tkinter Python library used for the GUI. Project currently used as a showcase in Intro to Comp. Sci class
	\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% Research Experience
%----------------------------------------------------------------------------------------
\begin{rSection}{Research}

	\textbf{Packet Trace Anonymization} \hfill Dec 2022 - May 2023 \\
	NYU Shanghai Computer Science Department - Advised by Prof. Guyue (Grace) Liu \hfill \textit{Shanghai, China}
	\begin{itemize}
		\item Built, modified, and tested network packet anonymization tools. Analyzed and compared their TCP/IP anonymization policies by conducting literature review, analyzing source code, and reading documentation.
		\item Using methodologies from tcpdpriv, tcpmkpub, and tcpdpriv to develop new secure packet anonymizer in C.
	\end{itemize}

	\textbf{Crypto Asset Rating Methodology Framework} \hfill May 2022 - Jan 2023 \\
	Dean’s Undergraduate Research Fund - Advised by Prof. Jiding Zhang \hfill \textit{Shanghai, China}
	\begin{itemize}
		\item Investigated how crypto rating methodologies can be improved through a holistic overview of the project, conducting data analysis on off chain metrics and on chain data to derive a performance rating, and using smart contract code auditing to determine a security rating.
		\item Developed smart contract applications and wrote tests with code coverage as a part of understanding full stack smart contract development and security practices.
	\end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
% Leadership Positions
%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership Positions}

	\textbf{President} \hfill May 2022 - May 2023 \\
	Undergraduate Business Association (UBA) @ NYU Shanghai \hfill \textit{Shanghai, China}
	\begin{itemize}
		\item Managed a club of 80+ members that held workshop, speaker series, and mentorship events on a weekly basis.
		\item Hosted inaugural UBA Spring Business Competition with data analysis, investing, and marketing tracks
		\item Our organization's impact on campus was recognized with the "Trailblazer" award, given to the most innovative and pioneering student organization in NYU Shanghai.
	\end{itemize}

	\textbf{Orientation Ambassador Captain} \hfill Mar 2022 - Sep 2022 \\
	New Student Programs @ NYU Shanghai \hfill \textit{Shanghai, China}
	\begin{itemize}
		\item Led a team of eight Orientation Ambassadors over four months to plan and host a Game Night during Freshmen Orientation Week, one of the four major OA organized events.
		\item Primarily delegated tasks, managed budget, and coordinated with Student Life staff to achieve a successful event.
	\end{itemize}

	\textbf{Class of 2025 President} \hfill Sep 2021 - May 2022 \\
	Student Government @ NYU Shanghai \hfill \textit{Shanghai, China}
	\begin{itemize}
		\item Led the organization and planning of NYU Shanghai’s week-long Spirit Week event and received over 100+ registered participants on kick-off day.
		\item Worked with the Class Engagement Board to plan and host a week of online events to support NYU Shanghai students during the 2022 Shanghai Lockdown.
		\item Served as the voice of my class and aggregated questions and concerns from the student body, and presented them, in the form of a report, at weekly student government meetings.
	\end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
%	Technical Skills
%----------------------------------------------------------------------------------------
\begin{rSection}{Technical Skills}
	\textbf{Programming Languages}{: Python (fluent), SQL (fluent), HTML/CSS (proficient), Solidity (proficient), C (prior experience),  Javascript (prior experience), Shell  (proficient), Lua (prior experience)} \\
	\textbf{Frameworks and Libraries}{: FastAPI, LangChain, Pytest, Flask, Hardhat, Pandas, Matplotlib, Numpy} \\
	\textbf{Developer Tools}{: Git and Github, Docker, Jenkins, Debian Linux, venv/Poetry, Vim, Vscode} \\
	\textbf{Cloud/Databases}{: MySQL, Redis, Redis Stack Server, Google Cloud BigQuery} \\
	\textbf{Coursework}{: Databases, Computer Architecture, Data Structures, Discrete Math, Linear Algebra} \\
\end{rSection}

%----------------------------------------------------------------------------------------
%	Honors and Awards
%----------------------------------------------------------------------------------------
\begin{rSection}{Honors and Awards}
	\begin{itemize}
		\item \textbf{Leadership in Action}{: Outstanding individual leadership in NYUSH student organizations} \hfill April 2023
		\item \textbf{Recognition Award}{: Excellent academic performance and contributions to the NYUSH community} \hfill July 2022
	\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Hobbies and Interests
%----------------------------------------------------------------------------------------
\begin{rSection}{Hobbies and Interests}
	\begin{itemize}
		\item \textbf{Leadership in Action}{: Outstanding individual leadership in NYUSH student organizations} \hfill April 2023
		\item \textbf{Recognition Award}{: Excellent academic performance and contributions to the NYUSH community} \hfill July 2022
		\item \textbf{Areas of Interest}{: Blockchain Development, Zero Knowledge Proof Applications, Backend Web Development}
	\end{itemize}
\end{rSection}

\end{document}
